---
editor: source
engine: knitr
filters:
  - webr-teachr
  - quiz-teachr
webr:
  packages: ["kofdata"]
  autoload-packages: false
---


# Git Setup

In this exercise we will test how well you know how to set up git in your working directory.

We will do this by looking at a specific example: 

Let's say, you and your classmates are supposed to be working on a Data Analytics and Visualisation task using the built-in `mtcars` dataset, where each of you are working on a different part of the task. You come up with the idea to use git to help keep track of different versions when working together.

```{r setup, include = FALSE}
library(kofdata)
# baro <- get_collection("ogd_ch.kof.barometer")
# print(baro)
# to print only part of the tslist
# baro_df <- as.data.frame(baro)
# print(baro_df[1:20, ])
```
```{r message = FALSE, warnings = FALSE}
head(mtcars)
```


## Exercise 1

How would you set up git in your working directory ?

::: {.callout-caution}
## Your turn!
Identify the set of commands needed to set up git on your machine!
:::

:::{.quiz-multichoice}
- [X] [`git init`]{hint="o"}
- [ ] [`git configuration`]{hint="x"}
- [ ] [`git start`]{hint="x"}
- [ ] [`git add`]{hint="x"}
:::


## Exercise 2

Let's say you changed, added or removed some files in the course of your work. How will you make these changes known to your colleagues?

::: {.callout-caution}
## Your turn!
Identify the commands needed to share your changes with others!
:::

:::{.quiz-multichoice}
- [X] [`git add`]{hint="o"}
- [ ] [`git final`]{hint="x"}
- [X] [`git commit`]{hint="o"}
<!-- TODO: determine whether you need to add the whole command, e.g. `git commit -m "xyz"` -->
- [ ] [`git pull`]{hint="x"}
- [X] [`git push`]{hint="o"}
:::

# Git Collaboration 
Now that you've set up your repository and shared your first commit with your teammates, you want to work on them together, and possibly simultaneously. 

## Exercise 1
How do you go about ensuring that you don't get in eachothers way when working?

:::{.quiz-multichoice}

- [X] [Create a new branch]{hint="o"}
- [ ] [Create a new repository]{hint="x"}
- [ ] [Proceed as is]{hint="x"}
:::

## Exercise 2

Let's say you while you were away, you aren't sure whether your teammates were working on your project or not. What do you do before working again?

:::{.quiz-multichoice}

- [ ] [Ask them]{hint="x"}
- [X] [`git pull`]{hint="o"}
- [ ] [`git push`]{hint="x"}

:::

<!-- # Git Merge Conflicts

You and your colleagues were dilligent in your collaboration, but for some unknown reason, you still get the following output when trying to push your changes:

```bash
CONFLICT (content): Merge conflict in file-name.txt
Automatic merge failed; fix conflicts and then commit the result.
```

How would you go about fixing this?

:::{.quiz-multichoice}

- [X] [check in which file the conflict happened]{hint="o"}
- [X] []{hint="o"}
- [ ] [`git push`]{hint="x"}

::: -->



# Git Diverging Branches

You and a colleague have been working on a project, but someone forgot to pull before re-starting the work. 
Now Git tells you that you have diverging branches. How do you deal with this issue?

## Exercise 1

```bash
On branch main
Your branch and 'origin/main' have diverged,
and have 1 and 2 different commits each, respectively.
```

:::{.quiz-multichoice}
- [ ] [`git pull`]{hint="x"}
- [X] [`git rebase`]{hint="o"}
- [X] [`git merge`]{hint="o"}
:::
